[Draft Title] Spatial Temporal Event Spotting in Volleyball Videos

### 2024-10-15 Paper.tex
Update author affiliation and keywords in Paper.tex

\author{\authorname{Hoang Quoc Nguyen\sup{1}\orcidAuthor{0000-0000-0000-0000}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
\affiliation{\sup{1}Institute of Problem Solving, XYZ University, My Street, MyTown, MyCountry}
\affiliation{\sup{2}Department of Computing, Main University, MySecondTown, MyCountry}
\email{523503, second\_author\}@kist.re.kr, third\_author@dc.mu.edu}
}

\keywords{The paper must have at least one keyword. The text must be set to 9-point font size and without the use of bold or italic font style. For more than one keyword, please use a comma as a separator. Keywords must be titlecased.}

@@

\section{\uppercase{Manuscript Preparation}}

@@

\section{\uppercase{Copyright Form}}

@@

\section{\uppercase{Conclusions}}
\label{sec:conclusion}

@@

If any, should be placed before the references section
without numbering. To do so please use the following command:
\textit{$\backslash$section*\{ACKNOWLEDGEMENTS\}}

@@

If any, the appendix should appear directly after the
references without numbering, and not on a new page. To do so please use the following command:
\textit{$\backslash$section*\{APPENDIX\}}

>>>>

\author{\authorname{Hoang Quoc Nguyen\sup{1}\orcidAuthor{0009-0002-2004-9285}, Second Author Name\sup{1}\orcidAuthor{0000-0000-0000-0000} and Third Author Name\sup{2}\orcidAuthor{0000-0000-0000-0000}}
\affiliation{\sup{1}Korea Institute of Science and Technology, Seoul, Republic of Korea}
\affiliation{\sup{2}Department of Computing, Main University, MySecondTown, MyCountry}
\email{523503, second\_author\}@kist.re.kr, third\_author@dc.mu.edu}
}

\keywords{Temporally Precise Spotting, Video Understanding, Spatial Temporal Event Spotting, Volleyball, Sport, Deep Learning}

@@

\section{\uppercase{Related work}}

@@

\section{\uppercase{PROPOSED METHOD}}

@@

\section{\uppercase{EXPERIMENTS}}
\label{sec:experiments}

\section{\uppercase{CONCLUSIONS}}
\label{sec:conclusions}

@@

If any, should be placed before the references section
without numbering. To do so please use the following command:

% \textit{$\backslash$section*\{ACKNOWLEDGEMENTS\}}

@@

If any, the appendix should appear directly after the
references without numbering, and not on a new page. To do so please use the following command:
% \textit{$\backslash$section*\{APPENDIX\}}
